Looking for CDI Bias: WG Comprehension

### 2021-08-07 02-preliminary-WGcomp.Rmd
minor edits

@@

>>>>

# Takehome: by model comparison, we find that equal slopes (across sex) and equal variance, but varying group means (and item difficulties) are justified.

@@

Extracting the estimated ability intercept for males from mg3: `r round(coef(mg3)[["Male"]]$GroupPars[1],2)`. 
(Why is this positive? Females should have higher ability (see plot).)
